# Reproducible Research: Peer Assessment 1

##Loading data

```{r}
Data <- read.csv("activity.csv")
```

##What is mean total number of steps taken per day?

###Total number of steps taken per day
```{r}
daily.total <- aggregate(Data$steps, list(Data$date), sum)
colnames(daily.total) <- c("Date", "Steps")
```


```{r}
with(daily.total, {
      par(oma=c(2,0,0,0), las=2, font.lab=2, cex.axis=0.5 )
      barplot(
      height=Steps,
      col=c("blue"),
      main="Total Steps",
      xlab="Day",
      ylab="Number of steps",
      names.arg=Date,
      space=c(0)
    )
})
```

### Mean of total steps per day
```{r}
daily.mean <- mean(daily.total$Steps, na.rm=TRUE)
daily.mean
```

### Median of total steps per day
```{r}
daily.median <- median(daily.total$Steps, na.rm=TRUE)
daily.median
```

##What is the average daily activity pattern?

###Here we find the mean steps taken for eatch 5-minute time interval.

###Generate the mean number of steps taken for each 5-minute interval.
```{r}
pattern <- aggregate(
    data=Data,
    steps~interval,
    FUN=mean,
    na.action=na.omit
)
colnames(pattern) <- c("Interval", "Average.Steps")
```

###Time-Series plot 
```{r}
with(pattern, {
    plot(
      x=Interval,
      y=Average.Steps,
      type="l",
      main="Average Steps Time-Series",
      xlab="Interval",
      ylab="Average Steps"

    )
})
```

###5-minute interval with the maximum number of steps
```{r}
Max <- pattern[pattern$Average.Steps==max(pattern$Average.Steps),]
Max
```

###The interval 835-840 minutes shows maximum number of steps.

##Imputing missing values

###Total number of missing values.
```{r}
NAcount <- nrow(subset(Data, is.na(Data$steps)))
NAcount
```

### Filling NA values with average 5-minute interval valuesr.
```{r}
NAsub <- data.frame(Data$steps)
NAsub[is.na(NAsub),] <- ceiling(tapply(X=Data$steps,INDEX=Data$interval,FUN=mean,na.rm=TRUE))
newData <- cbind(NAsub, Data[,2:3])
colnames(newData) <- c("Steps", "Date", "Interval")
```

###Data with substituted NA
```{r}
newsubset <- aggregate(newData$Steps, list(newData$Date), sum)
colnames(newsubset) <- c("Date", "Steps")

```


```{r}
with(newsubset, {
      par(oma=c(2,0,0,0), las=2, font.lab=2, cex.axis=0.5 )
      barplot(
      height=Steps,
      col=c("blue"),
      main="Total Steps",
      xlab="Day",
      ylab="Number of steps",
      names.arg=Date,
      space=c(0)
    )
})
```

### Mean of total steps per day
```{r}
new.mean <- mean(newsubset$Steps, na.rm=TRUE)
new.mean
```

### Median of total steps per day
```{r}
new.median <- median(newsubset$Steps, na.rm=TRUE)
new.median
```

###By filling the missing values both the mean and median values were slightly altered.

##Are there differences in activity patterns between weekdays and weekends?
